\textbf{Matching the forecast horizon with the relevant spatial and temporal processes and data sources}

### 2019-12-13 doc/manuscript.tex
final edits

Whether historical dynamics, contemporary spatial patterns, or some combination of the two will serve as the best source of 
information for forecasting may depend on how far into the future we are attempting to forecast \citep{harris_forecasting_2018}. 
This potential dependency on the ``forecast horizon'' (\textit{sensu} \citealt{Hyndman2018})
reflects lags in the response of ecological conditions to environmental change, shifts in the importance of ecological processes with
time scale \citep{levin_1992,rosenzweig_1995}, and differences between time-series and spatial gradients in the range of 
environmental conditions represented in observed data (Fig. \ref{fig:fast-slow-concept}).
At short forecast horizons (days to years), dynamics will reflect physiological and demographic responses and interactions
among the organisms present at a site more than temporal turnover of genotypes or species, 
environmental conditions are likely to stay within the range of historical variation, 
and the current state of the system is likely to capture the influence of unmeasured processes. As a result, 
for near-term forecasts time-series approaches may capture the key dynamics and provide accurate predictions.

@@

In each case study, we simulated the effects of an increase in temperature on simple systems with known dynamics.
The truth is represented by a simulation model that is mechanistic for at least one important process, 
but we treat the data-generating model as unknown when analyzing the data and we assumed that perfectly recovering the mechanisms
it contains would not be possible in practice. We began each simulation
under a stationary distribution of annual temperatures, allowing the system to equilibrate; we call this the baseline phase. 
We then increased temperature progressively over a period of time, followed by a second period of stationary, now elevated, temperature. 
The objective was to forecast the response of the system to the temperature increase based on spatial and/or temporal data 
``sampled" from the simulation during the baseline period.

@@

Evolutionary adaptation is a key uncertainty in predicting how environmental change will impact a focal population at a given location \citep{Hoffmann2011}. Like the shifts in species composition illustrated in the previous example, shifts in genotype frequencies can also influence dynamics and forecasts at different time scales. Although shifts in genotype frequencies at the population level are analogous to changes in species composition at the community level, the mechanisms are distinct: heterozygosity and genetic recombination have no analogue at the community level. We demonstrate how these processes influence short and long-term forecasts with a standard eco-evolutionary simulation model for a hypothetical annual plant population in which fecundity is temperature dependent, and different genotypes have different temperature optima (Fig. \ref{fig:evo_evo_spatial_temporal_models}A). Our model describes how the local density of each genotype changes between years, which depends on temperature and genotype densities in the previous year. Transient temporal dynamics are computed directly from the model; these dynamics are the basis for the temporal statistical model. To create a spatial gradient, we simulated the equilibrium density of each genotype in a series of local populations experiencing different mean temperatures. The pattern of equilibrium densities across the mean annual temperature gradient is the basis for our spatial statistical model: cold sites will be dominated by the cold-adapted homozygous genotype, warm sites will be dominated by the heat-adapted homozygous genotype, and intermediate sites will be dominated by the heterozygous genotype (Fig. \ref{fig:evo_evo_spatial_temporal_models}B). The full description of the eco-evolutionary simulation model is provided in SI Appendix \ref{eco-evo}.

>>>>

Whether historical dynamics, contemporary spatial patterns, or some combination of the two will serve as the best source of 
information for forecasting may depend on how far into the future we are attempting to forecast \citep{harris_forecasting_2018}. 
This potential dependency on the ``forecast horizon'' (\textit{sensu} \citealt{Hyndman2018})
reflects lags in the response of ecological conditions to environmental change, shifts in the importance of ecological processes with
time scale \citep{levin_1992,rosenzweig_1995}, and differences between time-series and spatial gradients in the range of 
environmental conditions represented in observed data (Fig. \ref{fig:fast-slow-concept}).
At short forecast horizons (days to years), dynamics will reflect physiological and demographic responses and interactions
among the organisms present at a site more than temporal turnover of genotypes or species; 
environmental conditions are likely to stay within the range of historical variation; 
and the current state of the system is likely to capture the influence of unmeasured processes. As a result, 
for near-term forecasts time-series approaches may capture the key dynamics and provide accurate predictions.

@@

In each case study, we simulated the effects of an increase in temperature on simple systems with known dynamics.
The truth was represented by a simulation model that was mechanistic for at least one important process, 
but we treated the data-generating model as unknown when analyzing the data and we assumed that perfectly recovering the mechanisms
it contains would not be possible in practice. We began each simulation
under a stationary distribution of annual temperatures, allowing the system to equilibrate; we call this the baseline phase. 
We then increased temperature progressively over a period of time, followed by a second period of stationary, now elevated, temperature. 
The objective was to forecast the response of the system to the temperature increase based on spatial and/or temporal data 
``sampled" from the simulation during the baseline period.

@@

Evolutionary adaptation is a key uncertainty in predicting how environmental change will impact a focal population at a given location \citep{Hoffmann2011}. Like the shifts in species composition illustrated in the previous example, shifts in genotype frequencies can also influence dynamics and forecasts at different time scales. Although shifts in genotype frequencies at the population level are analogous to changes in species composition at the community level, the mechanisms are distinct: heterozygosity and genetic recombination have no analogue at the community level. We demonstrate how these processes influence short and long-term forecasts with a standard eco-evolutionary simulation model for a hypothetical annual plant population in which fecundity is temperature dependent, and different genotypes have different temperature optima (Fig. \ref{fig:evo_evo_spatial_temporal_models}A).

Our model describes how the local density of each genotype changes between years, which depends on temperature and genotype densities in the previous year. Transient temporal dynamics are computed directly from the model; these dynamics are the basis for the temporal statistical model. To create a spatial gradient, we simulated the equilibrium density of each genotype in a series of local populations experiencing different mean temperatures. The pattern of equilibrium densities across the mean annual temperature gradient is the basis for our spatial statistical model: cold sites will be dominated by the cold-adapted homozygous genotype, warm sites will be dominated by the heat-adapted homozygous genotype, and intermediate sites will be dominated by the heterozygous genotype (Fig. \ref{fig:evo_evo_spatial_temporal_models}B). The full description of the eco-evolutionary simulation model is provided in SI Appendix \ref{eco-evo}.
